### 2014-03-15 Draft/abstract.tex
Fixing Partial Comments on Introduction
Revised Example, Related work, and background Section
Style Check
that and where left.

On the other hand, automatically inferring temporal constraints from API documents faces is challenging.
In particular, it is challenging to automatically 
identify the methods referenced in the natural language text to infer temporal constraints.

@@

To address the preceding challenge, we propose an natural-language-processing-based approach \tool,
to infer formal temporal constraints from natural language text of API documents. These constraints can be used (as input)
by various software testing and verification tools to detect defects in client code the APIs.
Our approach 
addresses the preceding challenge by building (and leveraging) domain-dictionaries systematically from API
documents and generic English dictionaries.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and \amazonAPI.
Our evaluation results are promising. In particular, \tool\ achieves an average of 65\% precision and 72\% recall
in inferring 63 temporal constraints from more than 3900 sentences of API documents.

>>>>

On the other hand, automatically inferring temporal constraints from API documents is challenging.
In particular, it is challenging to automatically 
identify the methods referenced in the natural language text to infer temporal constraints.

@@

To address the preceding challenge, we propose a natural-language-processing-based approach \tool,
to infer formal temporal constraints from natural language text of API documents. These constraints can be used (as input)
by various software testing and verification tools to detect defects in client code the APIs.
Our approach 
addresses the preceding challenge by building (and leveraging) domain-dictionaries systematically from API
documents and generic English dictionaries.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and \amazonAPI.
Our evaluation results are promising.
In particular, \tool\ achieves an average of 65\% precision and 72\% recall
in inferring 63 temporal constraints from more than 3900 sentences of API documents.

### 2014-03-15 Draft/approach.tex
Minor Fixes
Revised Example, Related work, and background Section
Style Check
that and where left.

\section{\tool\ Design}
\label{sec:approach}
%\vspace{-2mm}

@@

In particular, we use n-gram based approach as means to achieve this reduction. 
In the fields of computational linguistics and probability, an n-gram is a contiguous sequence of n words from a given sequence of text or speech. 
We first calculate the most frequently occurring n-grams in the text body. 
In particular, we are interested in the n-grams of length 4 or greater to achieve a reasonable reduction. 
We then prune the list of n-grams based on a subsumption. 
We consider a n-gram of length k ($n_k$) to subsume n-gram of length k-1 ($n_{k-1}$) iff $n_{k-1}$ is a substring of ($n_k$) and the frequency of occurrence of $n_{k-1}$ equals frequency of occurrence of $n_{k}$.
Finally, we rank the list of n-grams based on the frequency of their occurrence in the text, and select top-k n-grams for reduction.
For instance, \textit{Amazon Simple Storage Service}, \textit{an I/O Error Occurs}, and \textit{end of stream} are the examples of such n-grams detected by our approach.
%\begin{figure}[t]
%\begin{CodeOut}
%\begin{alltt}
%01: 
%04:
%\end{alltt}
%\end{CodeOut}\vspace*{-2ex}
%\caption{\label{fig:methodAPI} The method description of the \CodeIn{DefineObjectProperty} method in Facebook API}\vspace*{-4ex}
%\end{figure}
\\
\textbf{Prototype Implementation.}
Currently our prototype implementation works with online \amazon\ and JDK API. 
However, almost all of the developer documents are provided online as structured webpages.
Thus, current implementation of preprocessor can be easily extended to extract the desired information from any API developer documents.

@@

Finally, to achieve  n-gram reduction we used Apache Lucene$^{\textregistered}$~\cite{lucene}.
Apache Lucene is a high-performance, full-featured text search engine library written entirely in Java.
It is a technology suitable for nearly any application that requires full-text search, especially cross-platform.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence within each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
However, this component can be implemented using any other existing NLP libraries or approachs.
In particular, we annotate each sentence with POS tags, named-entity annotations and Stanford-typed dependencies.
For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

@@

\begin{enumerate}
	\item The sentence is not from parameter summary or return variable summary.
	Typically such sentences describe pre-post conditions as opposed to temporal constraints this approach addresses.
	\item The sentences contains modal modifiers such as ``\textit{can, could, may, must, should}'' expressing necessity.
	Typically, presence of such modal modifier is a strong indicator of presence of constraints imposed by an API developer
	\item If the sentence does not contain modal modifiers described previously, sentence must contain temporal modifier relationship, identified by Stanford-typed dependency parser.
	Typically, presence of temporal modifier is an indicator of presence of temporal information.  
	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``\textit{if}''.
\end{enumerate}

@@

Specification extractor then uses the semantic graph to determine
if a candidate sentence is a specification sentence and if so extract
the action that should be performed prior to the method the sentence
belongs to. Algorithm~\ref{alg:SenAnnotaator} describes this action extraction
process.

@@

The algorithm accepts the list of methods as an input produces a graph with
the nodes representing methods in an API and the directed edges representing temporal constraints.
First, a index is created based on the return types of the method (Line 2).
Second, all methods in an API are added to an unconnected graph (Line 3-4).
Then, for every public method in the input list, the algorithm checks the types
of the input parameters and constructs and directed edge from all the methods whose return value
have the same type to the method in question (Line 14- 20).
The algorithm does not take into consideration the basic parameter types such as integer, string (Line 15).
Additionally, an edge is created from the constructors of a class to the non static members methods of a class (Line 8 -13).
The resultant graph is then returned by the algorithm.

>>>>

\section{Approach Overview}
\label{sec:approach}
%\vspace{-2mm}

@@

In particular, we use n-gram based approach to achieve this reduction. 
In the fields of computational linguistics and probability, an n-gram is a contiguous sequence of n words from a given sequence of text or speech. 
We first calculate the most frequently occurring n-grams in the text body. 
In particular, we are interested in the n-grams of length 4 or greater to achieve a reasonable reduction. 
We then prune the list of n-grams based on a subsumption. 
We consider an n-gram of length k ($n_k$) to subsume n-gram of length k-1 ($n_{k-1}$) iff $n_{k-1}$ is a substring of ($n_k$) and the frequency of occurrence of $n_{k-1}$ equals frequency of occurrence of $n_{k}$.
Finally, we rank the list of n-grams based on the frequency of their occurrence in the text, and select top-k n-grams for reduction.
For instance, \textit{Amazon Simple Storage Service}, \textit{an I/O Error Occurs}, and \textit{end of stream} are the examples of such n-grams detected by our approach.
%\begin{figure}[t]
%\begin{CodeOut}
%\begin{alltt}
%01: 
%04:
%\end{alltt}
%\end{CodeOut}\vspace*{-2ex}
%\caption{\label{fig:methodAPI} The method description of the \CodeIn{DefineObjectProperty} method in Facebook API}\vspace*{-4ex}
%\end{figure}
\\
\textbf{Prototype Implementation.}
Currently our prototype implementation works with online \amazon\ and JDK API. 
However, almost all of the developer documents are provided online as structured webpages.
Thus, current implementation of preprocessor can be easily extended to extract the desired information from any API developer documents.

@@

Finally, to achieve  n-gram reduction we used Apache Lucene$^{\textregistered}$~\cite{lucene}.
Apache Lucene is a high-performance, full-featured text search engine library written entirely in Java.
Lucene is a technology suitable for nearly any application that requires full-text search, especially cross-platform.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence within each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
However, this component can be implemented using any other existing NLP libraries or approaches.
In particular, we annotate each sentence with POS tags, named-entity annotations and Stanford-typed dependencies.
For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

@@

\begin{enumerate}
	\item The sentence is not from parameter summary or return variable summary.
	Typically such sentences describe pre-post conditions as opposed to temporal constraints this approach addresses.
	\item The sentences contains modal modifiers such as ``\textit{can, could, may, must, should}'' expressing necessity.
	Typically, presence of such modal modifier is a strong indicator of presence of constraints imposed by an API developer
	\item If the sentence does not contain modal modifiers described previously, sentence must contain temporal modifier relationship, identified by Stanford-typed dependency parser.
	Typically, presence of temporal modifier is an indicator of presence of temporal information.  
	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``\textit{if}'' and ``\textit{whether}''.
\end{enumerate}

@@

Specification extractor then uses the semantic graph to determine
whether a candidate sentence is a specification sentence and if so extract
the action that should be performed prior to the method the sentence
belongs to. Algorithm~\ref{alg:SenAnnotaator} describes this action extraction
process.

@@

The algorithm accepts the list of methods as an input produces a graph with
the nodes representing methods in an API and the directed edges representing temporal constraints.
First, an index is created based on the return types of the method (Line 2).
Second, all methods in an API are added to an unconnected graph (Line 3-4).
Then, for every public method in the input list, the algorithm checks the types
of the input parameters and constructs and directed edge from all the methods whose return value
have the same type to the method in question (Line 14- 20).
The algorithm does not take into consideration the basic parameter types such as integer, string (Line 15).
Additionally, an edge is created from the constructors of a class to the non static members methods of a class (Line 8 -13).
The resultant graph is then returned by the algorithm.

### 2014-03-15 Draft/background.tex
Style Check
that and where left.

\textbf{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}. The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks. It provides a hierarchical structure for the dependencies with precise definitions of what each dependency means, thus facilitating machine based manipulation of natural language text.

@@

\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However, as mentioned previously, POS tagging works well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

Consider the word \CodeIn{POST} for instance. 
The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

@@

\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
This technique accepts the syntax-annotated sentences and builds a First-Order-Logic(FOL) representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques. 
The shallow parser itself is implemented as a sequence of cascading finite state machines based on the functions of stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

>>>>

\textbf{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}. The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks. It provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine based manipulation of natural language text.

@@

\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However, as mentioned previously, POS tagging works satisfactorily on well written news articles which does not necessary entail that the tagging works satisfactorily on domain specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

Consider the word \CodeIn{POST} for instance. 
The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

@@

\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
This technique accepts the syntax-annotated sentences and builds a First-Order-Logic(FOL) representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques. 
The shallow parser itself is implemented as a sequence of cascading finite state machines based on the function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

### 2014-03-15 Draft/evaluation.tex
Fixed bib entries and references
Minor Fixes
Style Check
that and where left.

\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline API & Mtds & Sen & Sen$_C$ & Sen$_{ICON}$ & TP & FP & FN & P(\%) & R(\%) & F$_S$(\%) & Spec$_{ICON}$ & Acc(\%)\\
\hline 
\hline java.io &  & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 & 56 & 71.8\\ 
\hline AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
\hline Total &  & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
\hline
%----------------- END TABLE DATA ------------------------ 
\multicolumn{13}{p{6.5in}}{\small
$^*$ Column average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences;
Sen$_{ICON}$: Total no. of constraint Sentences identified by \tool; 
TP: Total no. of True Positives; FP: Total no. of False Positives; FN: Total no. of False Negatives;
P: Precision; R: Recall; F$_S$: F-Score; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table*}

@@

In this section, we compared the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system (referred to as type-enforced constraint). The constraints that are enforced by the type-system can be enforced by IDEs. Hence, for such types of constraints, we do not require sophisticated techniques like ICON. 
For \CodeIn{java.io}, we define a type-enforced constraint as a constraint that mandates a method M accepting input parameter I of type T to be invoked after (at least one) a method M0 whose return value is of type T. 
Since there are no types in REST APIs, for \CodeIn{Amazon S3}, we consider a constraint as a type-enforced constraint if it is implicit in the \CodeIn{CRUD} naming convention followed by REST operations. In particular, we consider a constraint as a type-enforced constraint, if the constraint mandates a DELETE, GET, or PUT operation on a resource to be invoked after a GET operation on the same resource.

>>>>

\begin{tabular}{lcccccccccccc}
\topline
\headcol API & Mtds & Sen & Sen$_C$ & Sen$_{ICON}$ & TP & FP & FN & P(\%) & R(\%) & F$_S$(\%) & Spec$_{ICON}$ & Acc(\%)\\
\midline 
java.io & 662 & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 & 56 & 71.8\\ 
\rowcol AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
Total & 713 & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{13}{p{6.5in}}{\small
$^*$ Column average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences;
Sen$_{ICON}$: Total no. of constraint Sentences identified by \tool; 
TP: Total no. of True Positives; FP: Total no. of False Positives; FN: Total no. of False Negatives;
P: Precision; R: Recall; F$_S$: F-Score; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table*}

@@

In this section, we compared the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system (referred to as type-enforced constraint). The constraints that are enforced by the type-system can be enforced by IDEs. Hence, for such types of constraints, we do not require sophisticated techniques like ICON. 
For \CodeIn{java.io}, we define a type-enforced constraint as a constraint that mandates a method M accepting input parameter I of type T to be invoked after (at least one) a method M0 whose return value is of type T. 
Since there are no types in REST APIs, for \CodeIn{Amazon S3}, we consider a constraint as a type-enforced constraint if the constraint is implicit in the \CodeIn{CRUD} naming convention followed by REST operations. In particular, we consider a constraint as a type-enforced constraint, if the constraint mandates a DELETE, GET, or PUT operation on a resource to be invoked after a GET operation on the same resource.

### 2014-03-15 Draft/example.tex
Style Check
that and where left.

We next present a real world example to motivate our approach.
In particular, through the example, we demonstrate that developers often ignore the temporal constraints of an API described in the documentation.
We suspect the reason for this phenomena is that the documentation is often verbose and the information is distributed across various pages.
For instance, the PDF version of the documentation for \amazonAPI\footnote{\url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}} spans 278 pages.
Developers often may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
resulting in defective client applications that invoke API methods in sequences prohibited by documentation.

@@

Consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the constraints in \amazon.
The API document pertaining to the  delete bucket functionality clearly states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed but one of the responses on the forum encouraged the person asking query to switch to another product,
thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.

The preceding issue can be easily detected using formal analysis tools.
For instance, a specification rule (a temporal constraint) can be added to a static checker to verify
the presence of a call to delete object functionality before the call to delete bucket functionality.
However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
In next section, we briefly discuss the related work pertinent to our proposed approach.

>>>>

We next present a real world example to motivate our approach.
In particular, through the example, we demonstrate that developers often ignore the temporal constraints of an API described in the documentation.
We suspect the reason for this phenomena is that the documentation is often verbose and the information is distributed across various pages.
For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.
Developers often may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
resulting in defective client applications that invoke API methods in sequences prohibited by documentation.

@@

Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/}}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the constraints in \amazon.
The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed but one of the responses on the forum encouraged the person asking query to switch to another product,
thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.

The preceding issue can be easily detected using formal analysis tools.
For instance, a specification rule (temporal constraint) can be added to a static checker to verify
the presence of a call to delete object functionality before the call to delete bucket functionality.
However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
In next section, we briefly discuss the related work pertinent to our proposed approach.

### 2014-03-15 Draft/introduction.tex
Style Check
that and where left.

Despite being desirable, most API's do not have formal constraints.
In contrast, API developers commonly describe correct temporal usage in natural language text in API documents.
Typically, such documents are provided to client-code developers through online access, or are shipped with the API code.
%For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
For a method under consideration, an API document may describe both the constraints on that method parameters as well as the temporal constraints in terms of the methods must be invoked pre/post the method.
We observed that a eminent portion (roughly 12\%) of the sentences (that describe some sort of constraints) in \amazonAPI\ documentations describe temporal constraints.
Although API documents contain temporal constraints, existing formal analysis tools accept only formal constraints but not informal constraints written in natural language.

>>>>

Despite being desirable, most API's do not have formal constraints.
In contrast, API developers commonly describe correct temporal usage in natural language text in API documents.
Typically, such documents are provided to client-code developers through online access, or are shipped with the API code.
%For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
For a method under consideration, an API document may describe both the constraints on that method parameters as well as the temporal constraints in terms of the methods must be invoked pre/post the method.
We observed that an eminent portion (roughly 12\%) of the sentences (that describe some sort of constraints) in \amazonAPI\ documentations describe temporal constraints.
Although API documents contain temporal constraints, existing formal analysis tools accept only formal constraints but not informal constraints written in natural language.

### 2014-03-15 Draft/related.tex
Style Check
that and where left.

%\subsection{Code Contracts - Formal Specifications}
% Define temporal constraints distinction
\textbf{Formal Specification}:
Contracts have become an a well-known mechanism for formally specifying functional behavior of the software. 
Contracts specify the behavior in terms of conditions that must hold before/after and during the execution of the method.
A significant amount of work has been done in automated inference of contracts.
Existing approaches use program analysis~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}
as means to automatically infer contracts.
However, recent studies~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA} demonstrate that a combination of developer-written and automatically extracted
contracts is the most effective approach for formally specifying the constraints on an API.
Since  our approach infers temporal constraint from API documents, we believe our approach can work in conjunction with existing approaches
to infer a compressive set of specifications.

@@

\textbf{Augmented Documentation}:
Improving the documentation related to an software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
(way of marking the specification sentences) in the default API documentation.
These directives are highlighted whenever they are displayed in the eclipse environment.
Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
thus allowing tool-based verification.
However, a developer has to manually annotate such directives.
In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.

>>>>

%\subsection{Code Contracts - Formal Specifications}
% Define temporal constraints distinction
\textbf{Formal Specification}:
Contracts have become a well-known mechanism for formally specifying functional behavior of the software. 
Contracts specify the behavior in terms of conditions that must hold before/after and during the execution of the method.
A significant amount of work has been done in automated inference of contracts.
Existing approaches use program analysis~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}
to automatically infer contracts.
However, recent studies~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA} demonstrate that a combination of developer-written and automatically extracted
contracts is the most effective approach for formally specifying the constraints on an API.
Since  our approach infers temporal constraint from API documents, we believe our approach can work in conjunction with existing approaches
to infer a compressive set of specifications.

@@

\textbf{Augmented Documentation}:
Improving the documentation related to a software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
(way of marking the specification sentences) in the default API documentation.
These directives are highlighted whenever they are displayed in the eclipse environment.
Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
thus allowing tool-based verification.
However, a developer has to manually annotate such directives.
In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
